%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Simplified resume subheading for better ATS parsing
% #1: Title (e.g., Company Name or Degree)
% #2: Date Range
% #3: Subtitle (e.g., Role or Major)
% #4: Location
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \textbf{#1} \hfill #2 \\
  \textit{\small#3} \hfill \textit{\small #4} \\
  \vspace{-7pt} % Adjust vertical spacing as needed
}

% Project heading (simplified for ATS)
% #1: Project Title and Technologies
% #2: Date Range
\newcommand{\resumeProjectHeading}[2]{
  \item
  \small#1 \hfill #2 \\
  \vspace{-7pt} % Adjust vertical spacing as needed
}

% Added this to remove 2nd line.
\newcommand{\resumeSubheadingTwo}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% Standard bullet point for better ATS parsing
\renewcommand\labelitemii{\textbullet}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING---------- (Slight modification: removed underline from contact links for potentially better parsing)
\begin{center}
    \textbf{\Huge \scshape Christian Wilkins} \\ \vspace{1pt}
    \small \href{mailto:christian.wilkins.careers@gmail.com}{christian.wilkins.careers@gmail.com} $|$
    \href{https://www.linkedin.com/in/christian--wilkins/}{linkedin.com/in/christian--wilkins/} $|$
    \href{https://github.com/christianwilkins}{github.com/christianwilkins} $|$
    \href{https://chriswiki.com/}{chriswiki.com} % Removed \phantom{/}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Michigan State University}{December 2025}
      {Bachelor of Science in Computer Science, Minor in Business - GPA 3.9}{East Lansing, MI}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{June 2025 -- August 2025}
      {JPMorganChase}{Columbus, OH}
    \resumeItemListStart
        \resumeItem{Developed an \textbf{AI-powered matching engine} using \textbf{scikit-learn, spaCy, and PostgreSQL} that streamlined internal job placements, winning first place at \underline{\href{https://www.linkedin.com/posts/indi-de-silva_at-jpmorganchase-our-internship-program-activity-7355579081490354177-NYLE}{JPMC Global Hackathon}} out of 1000+ participants.}
        \resumeItem{Optimized \textbf{AWS S3 data migrations} for concurrency by 95\% using \textbf{concurrent.futures and boto3} in \textbf{Python}, improving data processing efficiency through automated migration pipelines.}
        \resumeItem{Implemented \textbf{PactFlow \& Jules contract testing} framework across multiple \textbf{microservices}, reducing cross-team integration issues by 90\%.}
        \resumeItem{Built \textbf{RESTful APIs} using \textbf{Spring Boot and Java} for internal tooling, following enterprise security standards and best practices.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2024 -- August 2024}
      {Configura}{Grand Rapids, MI}
      \resumeItemListStart
        \resumeItem{Engineered a custom sales extension in a \textbf{75M+ line proprietary codebase (C\#/Java-like)}, collaborating daily with clients to integrate new functionalities that directly enabled the sale of their core product.}
        \resumeItem{Navigated a vast, undocumented system, proactively engaging senior engineers to ensure seamless integration.}
        \resumeItem{Pioneered novel hit detection for modeled spaces in CM, preventing impossible configurations and enhancing UX.}
      \resumeItemListEnd

\resumeSubheading
      {Undergraduate Research Assistant}{October 2023 -- April 2024}
      {Michigan State University}{East Lansing, MI}
      \resumeItemListStart
        \resumeItem{Processed HIPAA-compliant data for ML pipeline (Python, scikit-learn, NLP, CV) auto-grading medical exams.}
        \resumeItem{Achieved 89\% validation accuracy (93\% goal), reducing exam grading time from months to days.}
      \resumeItemListEnd

\resumeSubheading
      {Board Advisor \& Former President}{March 2024 -- Present}
      {\underline{\href{https://www.imagine-software.org/}{Imagine Software}}}{East Lansing, MI}
      \resumeItemListStart
        \resumeItem{Oversaw an internship-like experience for 60 students across 10 agile development teams, conducting bi-weekly technical reviews and mentoring sessions to ensure project delivery and skill development.}
        \resumeItem{Led organizational growth initiatives as President, achieving 100\% membership growth to 350+ members through targeted outreach campaigns and technical workshop programming.}
      \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\underline{\textbf {\href{https://github.com/keshavbabu/shellhacks/tree/main}{hurrycane}}} $|$ \emph{Swift, MongoDB, Firebase, Go, iOS}}{September 2024}
          \resumeItemListStart
            \resumeItem{Architected and developed \textbf{'hurrycane'} using \textbf{Swift iOS frontend and Go backend}, a real-time ride-sharing application with \textbf{MongoDB and Firebase} for emergency evacuations, \textbf{winning Waymo @ ShellHacks 2024}.}
            \resumeItem{Implemented \textbf{scalable, concurrent Go routing algorithms} for multi-stop emergency routes, optimizing continuous GPS location tracking and real-time coordinate updates.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\underline{\textbf {\href{https://www.notelify.co/}{Notelify}}} $|$ \emph{Next.js, React, Supabase, Figma, Typescript}}{October 2023 -- April 2024}
          \resumeItemListStart
            \resumeItem{Developed Notelify frontend (Next.js, React) and integrated cost-effective Mozilla Speech-to-Text API with OpenAI APIs (via prompt engineering) for automated meeting summaries. Experimented with machine learning.}
            \resumeItem{Automated note-taking via AI, reducing student effort by 95\%; won 'Best Use of AI' award (\$100).}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{RecycleMe} $|$ \emph{Flutter, Firebase, OpenAI APIs, Trello, Python, PyTorch, TensorFlow}}{October 2023 -- April 2024}
          \resumeItemListStart
            \resumeItem{Led a 5-member agile team to develop RecycleMe MVP (Flutter/Dart, Firebase) in 90 days, gamifying recycling via GPT-Vision for object recognition and custom dataset (90\% accuracy). Followed + Created a spec doc.}
            \resumeItem{Managed using Trello, fostering an environment for learning agile methodologies and full-stack development.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{ThinkedIn} $|$ \emph{Discord, LinkedIn, Mentorship}}{March 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Founded a \(\sim \)200 member organization providing career help and insight for increasing social media presence.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++, Go, HTML, Dart, SQL} \\
     \textbf{Technologies}{: Spring Boot, React.js, Node.js, AWS (S3, EC2, Lambda, RDS, DynamoDB), Docker, Kubernetes, Git, Firebase, PostgreSQL, MongoDB, RESTful APIs, Microservices, CI/CD, NumPy, Flutter, Linux, Jira} \\
     \textbf{Concepts}{: Full Stack Development, Cloud Computing, DevOps, Agile Development, Machine Learning, Data Structures \& Algorithms, Microservices Architecture, Contract Testing, Fintech, Data Migration, Observability} }}
 \end{itemize}
 
%
%-------------------------------------------
\end{document}
